---
title: "Assignment 8"
author: Artie Maharaj
date: April 6, 2020
output: html_notebook
---
This is my assignment 8 for EDRM 718

1. Write a function that will compute the total score for respondents on a Likert Scale

```{r}
Likert.Total.Score <- function(dataframe, numeric, vector) {
  
  #here is the function for the dataframe
  
  dataframe <-read.csv("data")
  
  #here is the function to call the number of scale items. 
  
  numeric = somenumber
  
  #here is the function for a numeric vector indicating which items should be reversed       scored
  
  new.data.frame <- dataframe
  
  new.data.frame[, c(qx,qy,qz)] <- x-new.data.frame[,c(qx,qy,qz)]
  
  #need to update the dataframe to reflect the updated reversed scored items. so this     
  #should just recode my scores in the dataframe. not sure if i need cbind here. 
  
  #need to sum total score across items
 total.scores <- rowSums(new.data.frame)
 
 new.data.frame <-cbind(new.data.frame,total.scores)
  
  return(new.data.frame)
 
}
```

2. Information for this question:
The csv file that was created is called: art.data.csv. 
Items: Q1-Q8
6 point scale [1,2,3,4,5,6]



```{r}

#Here is code to run the dataframe

likert.data <- read.csv("art.data.csv")

# I am not sure how, but I got a row of NAs so I had to remove it from the data frame.

likert.data= likert.data[-c(6),] 

#Here is code to run the scale

numeric = 6

# Here is a function to reverse code items Q2, Q4, Q7
new.likert.data <- likert.data
  
new.likert.data[,c(2, 4, 7)] <- abs(new.likert.data[,c(2, 4, 7)] -7)

#Here is code to calculate total scores for each respondent

total.scores <- rowSums(new.likert.data)

#Here is code to add in new column to the new.likert.data dataframe.  
new.likert.data <-cbind(new.likert.data,total.scores)


```

3. Use the hsb2 data and ggplot2 to construct a single scatterplot showing the relationship of science scores (response) to math scores (explantory) by gender. 

```{r}

```

4. Again, show the relationship of science scores to math scores by gender, but this time facet on gender to show separate scatterplots 

```{r}
library(tidyverse)

hsb2 <- read_csv("hsb2.csv")
hsb2

hsb2$gender <- factor(hsb2$female,
                   labels = c("male", "female"),
                   ordered = FALSE)

ggplot(data = hsb2) +
  geom_point(mapping = aes(x = science, y = math, color = gender))

```
5.
Using your ggplot2 cheat sheet and the hsb2 data, create a graph geom that was not mentioed in the lecture. Briefly describe what your graph is illustrating. 

```{r}

```

