---
title: "Assignment 8"
author: Artie Maharaj
date: April 6, 2020
output: html_notebook
---
This is my assignment 8 for EDRM 718

1. Write a function that will compute the total score for respondents on a Likert Scale

```{r}
Likert.Total.Score <- function(mydata, numeric, newvector) {
  
  #here is the function for the dataframe
  
  mydata <- as.data.frame(mydata)
  
  
#Create a numeric vector for the reversed scored items
  
  recode <- abs(mydata[,c(newvector)] - numeric)
  
  norecode <-mydata[,-newvector]
  
  recoded.data.frame <-cbind(norecode, recode)
  
#Add in row sums  

   total.scores <- rowSums(recoded.data.frame)
  
#Update the data frame to include total row score
   
   updated.data.frame <-cbind(recoded.data.frame, total.scores)
    
   return(updated.data.frame)
 
}
```

2. Information for this question:
The csv file that was created is called: art.data.csv. 
Items: Q1-Q8
6 point scale [1-6]

```{r}

#Here is code to read in the data. 

likert.data <- read.csv("art.data.csv")

# I am not sure how, but I got a row of NAs so I had to remove it from the data frame.

likert.data= likert.data[-c(6),] 

###Test function

Likert.Total.Score(likert.data, 6, c(2,4,7))

likert.function <-Likert.Total.Score(likert.data, 6, c(2,4,7))

write.csv(likert.function)

```
3.Use the hsb2 data and ggplot2 to construct a single scatterplot showing the relationship of science scores (response) to math scores (explantory) by gender.

```{r}
library(tidyverse)

hsb2 <- read_csv("hsb2.csv")
hsb2

hsb2$gender <- factor(hsb2$female,
                   labels = c("male", "female"),
                   ordered = FALSE)

ggplot(data = hsb2) +
  geom_point(mapping = aes(x = math, y = science, color = gender))

```

Again, show the relationship of science scores to math scores by gender, but this time facet on gender to show separate scatterplots 
```{r}
ggplot(data = hsb2) +
  geom_point(mapping = aes(x = math, y = science)) +
  facet_wrap(~ gender)
```

5.
Using your ggplot2 cheat sheet and the hsb2 data, create a graph geom that was not mentioed in the lecture. Briefly describe what your graph is illustrating. Tried out the jitter geom and the rug geom.

```{r}
ggplot(data= hsb2)+ 
 geom_jitter(mapping = aes(x= math, y= science)) +
  facet_wrap(~gender)

ggplot(data= hsb2)+ 
 geom_rug(mapping = aes(x= math, y= science)) +
  facet_wrap(~gender)
 


```

